Highlighting Disputed Claims on the Web

### 2009-10-28 papers/www_disputefinder/disputefinder.tex
Addressed comments from Tye and fixed bad quotes

Dispute Finder builds it's database of disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed. Dispute Finder identifies instances of disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of a subset of our claim database.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/highlight_abortion.png}
	\caption{A highlighted snippet that makes a disputed claim}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
	\caption{Popup interface with articles for and against a claim}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a "don't mark this" button}

@@

In the realm of News, Pew~\cite{pew-news} report that, while Internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible. Even when users are getting news from the websites of traditional news providers, it is likely that they read news from a variety of unfamiliar news sources~\cite{pew-news}, rather than the small set of newspapers and TV stations that they might have followed in the past.

@@

In this paper we describe Dispute Finder, a tool that alerts a user when information they read online is disputed by a source that they might trust. Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in, understand why other people hold different points of view, and avoid being mislead by misinformation.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/snippet_claim_article_fancy2.png}
	\caption{Snippets entail claims, which are entailed or contradicted by articles}
	\label{snippet_claim_article}
	\end{center}
\end{figure}

@@

{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust. Their are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic. A user may behave like a skeptical reader for some topics and not others. For example a user may be skeptical when reading about topics that affect them (e.g. health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that don't affect them (e.g. entertainment) or topics for 
\todo{Use interviews to get some actual observations here. These are just fillers.}

@@

Many users fall into neither of these two personas. If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then Dispute Finder is unlikely to be useful for them.

@@

Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic. Instead, the only way they can add promote an opinion is to link to an article from a trusted source that argues for that opinion. Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.

@@

Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as "is an example of", "supports", or "challenges". An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.

@@

\todo{Cite plagarism detection}
\todo{Talk about how our algorithm looks for key terms used in disputed claims}
\todo{Talk about how our first pass NLP algo is rather like }

@@

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/highlight_bar.png}
	\caption{Highlight and Notification Bar}
	\label{highlight_bar}
	\end{center}
\end{figure}

@@

The notification bar alerts the user that they should look out for highlighted snippets. Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors} or if the user is color blind. The notification bar also allows a user to step through the highlighted snippets on the page.

The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims. This allows a user to ignore disputed claims that are made by text that the user isn't interested in - such as user comments. The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it isn't making. In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the "report incorrect highlighting" button from the popup interface.

@@

\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}). For each article, the interface shows a summary sentence that captures the core argument used by the article. A user can add any web page as a supporting article by browsing to the page, selecting "use as evidence" from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
\end{description}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_evidence.png}
	\caption{Adding an article, with a summary sentence selected}
	\label{add_article}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/article_choose_claim.png}
	\caption{Choose how to connect an article with a claim}
	\label{article_choose}
	\end{center}
\end{figure}

@@

It is possible that the best solution would be a visualization that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and {\it why} the various sources held those opinions.

@@

We do not want the database of disputed claims to contain everything that has every been disputed by anyone. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence that the moon is made of cheese, but few people believe this claim is true. What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/add_claim_list.png}
	\caption{Interface for adding a new disputed claim manually}
	\label{add_claim}
	\end{center}
\end{figure}

Fortunately, several web sites already maintain databases of disputed claims, together with arguments against them. For example Snopes.com maintains a list of urban legends and Politifact.com maintains a list of false claims about politics. We automatically import all claims that either of these sites debunk into our database and treat the sites themselves as reliable sources about the claims they debunk. In the future we intend to also import claims from other such sites, and allow users to choose which feeds of disputed claims should be used to highlight snippets on pages they browse.

We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure\ref{add_claim}). The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org. It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim. When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_disputed.png}
	\caption{Explicit page marking}
	\label{mark_disputed}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/training2.png}
	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons}
	\label{training}
	\end{center}
\end{figure}

\begin{figure}[t]
	\begin{center}
	\includegraphics[width=7cm]{pictures/nlp_client_server2.png}
	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server}
	\label{nlp_client_server}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/paraphrases.png}
	\caption{Users can enter paraphrases of a claim to help the entailment algorithm}
	\label{paraphrases}
	\end{center}
\end{figure}

\begin{description}
\item[Explicit page marking:] The user explicitly marks a snippet on a page by selecting the snippet, and selecting "mark as disputed" from a context menu (Figure~\ref{mark_disputed}).

@@

\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browse, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}). A user can enter additional paraphrases of a claim to help the entailment algorithm (Figure~\ref{paraphrases}). This is the implementation used by the currently released version of Dispute Finder.
\end{description}

@@

The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm that is a common baseline in NLP. It divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for "hot terms" such as "Global Warming" that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

@@

%The Design of Dispute Finder has been influenced by several different kinds of input from potential users. We performed a series of "think aloud" user studies to evaluate the user interface, we circulated a survey among members of a local debate club, and we performed a series of interviews with people selected from those who completed the survey.
%
%\subsection{Survey}
%
%We circulated a survey amongst members of a local debate club - a set of people who we believe is a good match for our Skeptical Reader and Activist personas. They survey asked respondants to tell us how often they typically engaged in various behaviours on the web. Although the survey was too small to be statistically useful, the results gave some useful information that we believe is worth reporting.
%
%Most people 65\% said that some of the information they read is not trustworthy, but they know which sites they can trust. Nobody said that they trusted the most of the information they read. 17\% trust very little of the information they read, and 9\% feel confused about what they can trust.
%
%Everyone had used another source to double-check information they had read online. 74\% "often" search the web to find web pages that confirm a claim they have read. 64\% "often" check a website they trust. 55\% "sometimes" ask a friend and 55\% "sometimes" check a book.
%
%When deciding whether to trust a web site, the most important factor was whether the site was run by an organization they trusted (61\% often, 30\% sometimes), followed by whether the site was linked from another site they trusted (18\%,50\%), and whether the site was well written (18\%,50\%).
%
%% \subsection{Interviews}
%
%\todo{Do we have enough interview content to integrate it? Probably not yet...}
%\todo{Is the survey interesting enough to quote here? Only 23 people, and not exciting. Just quote inline with findings.}

We performed three qualitative "think aloud" user studies. The aim of these studies was to inform the iterative design of the Dispute Finder tool. The studies were not intended to validate the design of Dispute Finder as being correct. The only way we will be able to truly validate Dispute Finder is by having it be adopted by a large community of active users - something it is not yet mature enough for.

@@

For the first two studies, we recruited participants using Craigslist. We posted a message asking people to tell us how they used the web to form and promote their opinions, and used their responses to select people who we thought might fit our "skeptical reader" and "activist" personas. After these studies, we decided that the kind of person who looks for jobs of Craigslist is typically not a good fit for our personas, and so for the final study we instead used people we knew personally and thought fit our personas well. All study groups were small. The first study had twelve participants (five female, seven male), the second study had six participants (four female, two male), and the final study had six participants participants (all male).

Each batch of users was shown a different iteration of the Dispute Finder design. The first two batches used versions in which users marked snippets explicitly and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view. The final group used a version in which a textual entailment algorithm on the client was used to determine what to mark, and the popup window showed lists of sources that support or oppose the claim. We present the findings of the three user studies together. Where a comment refers to particular version we make this clear.

@@

We also conducted interviews with most of our user study participants, and six additional people, asking them how they use the web to form and promote their opinions.

@@

Response was generally positive, with many participants being very keen to use the tool soon. Several participants asked as to notify them when it is properly deployed. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

Most participants said that they would want to use Dispute Finder to tell them when information they read was disputed (skeptical reader). One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''. A smaller number said they would be likely to enter claims they disagreed with (activist). One participant who was a political blogger was very excited about the mark things he thought were lies.

@@

%In the first study, a user could mark a snippet by 
%
%In the interface used in the first two studies, a user could mark a snippet by selecting it, right clicking on it, and clicking "mark as disputed". They were then prompted to either select an existing claim or create a new one.

When marking a snippet on a particular page, users often did not appreciate that a claim should apply to more than one snippet. Several users tried to create a new claim with exactly the same text as the snippet they were marking, and several users asked why they had to "enter the text again". Similarly, several users got confused when a snippet made two different disputed claims. The correct behavior is to mark the same text with two different claims, but several participants tried to create a new compound claim such as "Global warming will cause X and Y".

@@

In the first two studies, the popup interface for a claim showed an argumentation graph. This graph connected the graphs in our database using "supports" or "opposes" links, and allowed each claim to also be associated with supporting articles. When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected. One user said "I can see myself getting addicted to this", and another said "it's very intuitive".

Users seemed to have difficulty creating such graph structures however. Several users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim. For example "Global warming is causing more hurricanes" does not support "Global warming is causing rising sea levels", but both support "Global warming is causing problems". Users correctly realized that the claims were related, but were not sure how best to connect them. Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. These findings are consistent with those of Isenmann and Reuter~\cite{Isenmann1997}.

@@

When using the article-list interface, several users got confused about whether an article supported or opposed a claim that was itself phrased in the negative. For example a user would mark an article that opposed global warming as opposing the claim "global warming is bad" because the article opposed global warming.

@@

Several users created claims that had ambiguous meanings. One user entered a disputed claim about "Wood", meaning the guitarist "Ronnie Wood" of the Rolling Stones. Similar problems occurred with claims that were specific to a particular country, or a particular point in time.

Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them or that they were expected to be knowledgeable about, but were less interested about applying it to pages about other topics, that they were less interested in. For topics that didn't affect them users felt that misinformation was "not important enough to bother with", or that they could "afford to be misinformed".

@@

\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple "supports"/"opposes" graph.}

@@

@@

Performing these tasks well is a hard problem, and we do not yet claim to have an implementation that is is good enough to be compelling for most users. We do however believe that Dispute Finder attacks an interesting problem that, if solved well, could significantly improve the utility of the web.

>>>>

Dispute Finder builds its database of disputed claims by crawling web sites that already maintain lists of disputed claims, and by allowing users to enter claims that they believe are disputed. Dispute Finder identifies instances of disputed claims by running a simple textual entailment algorithm inside the browser extension, referring to a cached local copy of a subset of our claim database.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/highlight_abortion.png}
	\caption{Dispute Finder highlights text snippets that make disputed claims.}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

In the realm of News, Pew~\cite{pew-news} reports that, while Internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible. Even when users are getting news from the websites of traditional news providers, it is likely that they read news from a variety of unfamiliar news sources~\cite{pew-news}, rather than the small set of newspapers and TV stations that they might have followed in the past.

@@

In this paper we describe Dispute Finder, a tool that alerts a user when information they read online is disputed by a source that they might trust. Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in by exposing them to different points of view.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/snippet_claim_article_fancy3.png}
	\caption{Snippets entail claims. Claims are entailed or contradicted by articles.}
	\label{snippet_claim_article}
	\end{center}
\end{figure}

@@

{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust. They are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic. A user may behave like a skeptical reader for some topics and not others. For example a user may be skeptical when reading about topics that affect them (e.g. health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that don't affect them (e.g. entertainment).

\todo{Move our personals to a ``people'' section}

\todo{Use interviews to get some actual observations here. These are just fillers.}

@@

Many users fall into neither of these two personas. If a user does not regularly read information online that they feel they need to need to understand well, or restricts their reading to sources that they believe they can trust, then they are unlikely to be interested in Dispute Finder.

@@

Unlike these annotation tools Dispute Finder does not allow a user to directly express their own opinions about a topic. Instead, the only way they can add or promote an opinion is to link to an article from a trusted source that argues for that opinion. Our interviews lead us to believe that most users would rather know the cases where a trusted source disagrees with what is being written, rather than when an unknown user disagrees.

@@

Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''. An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.

@@

\todo{Talk about what dispute finder does, and how it differs - maybe by moving this into the main system section}
\todo{Cite plagarism detection}
\todo{Talk about how our algorithm looks for key terms used in disputed claims}
\todo{Talk about how our first pass NLP algo is rather like }

@@

\todo{Talk about how this information was used in the design of Dispute Finder.}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/highlight_bar.png}
	\caption{Dispute Finder highlights text snippets that make disputed claims, and displays a notification bar to inform the user that they should look out for highlighted snippets.}
	\label{highlight_bar}
	\end{center}
\end{figure}

@@

The notification bar alerts the user that they should look out for highlighted snippets. Highlights can be difficult to see if the page is using a background that is similar to our highlight color\footnote{We tried to choose a color that is easily distinguished from most background commonly used background colors.} or if the user is color blind. The notification bar also allows a user to step through the highlighted snippets on the page.

The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims. This allows a user to ignore disputed claims that are made by text that the user isn't interested in - such as user comments. The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it isn't making. In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.

@@

\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}). For each article, the interface shows a summary sentence that captures the core argument used by the article. A user can add any web page as a supporting article by browsing to the page, selectinguse as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
\end{description}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_evidence.png}
	\caption{To add an article, select some summary text, and click ``use as evidence'' from the context menu.}
	\label{add_article}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/article_choose_claim.png}
	\caption{Choose how to connect an article with a claim.}
	\label{article_choose}
	\end{center}
\end{figure}

@@

It is possible that the best solution would be a visualization that made it easy for a user to see both {\it who} was supporting/opposing a particular claim, and what arguments were being put forward.

@@

We do not want the database of disputed claims to contain everything that has ever been disputed by anyone. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence that the moon is made of cheese, but few people believe this claim is true. What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/add_claim_list.png}
	\caption{A user can use this interface to add a new disputed claim manually.}
	\label{add_claim}
	\end{center}
\end{figure}

Fortunately, several web sites already maintain databases of disputed claims, together with arguments against them. For example Snopes.com maintains a list of urban legends and Politifact.com maintains a list of false claims about politics. We automatically import all claims that from these sites into our database. In the future we intend to also import claims from other such sites, and allow users to choose which feeds of disputed claims should be used to highlight snippets on pages they browse.

We also allow users to add their own disputed claims using the Dispute Finder web interface (Figure~\ref{add_claim}). The web interface is modeled after common issue-reporting software such as Uservoice.com and Bugzilla.org. It first encourages the user to search the existing database to see if their claim already exists, and then allows them to create a new claim. When the claim is first added it is marked with a warning, informing the user that the claim will not be highlighted for other users until they have added at least one opposing article.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/mark_disputed.png}
	\caption{Explicit page marking: select the text that makes a disputed claim and click ``this is disputed'' from the context menu.}
	\label{mark_disputed}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/training2.png}
	\caption{Bulk page marking and server-side classification: classifier guesses are shown below the choice buttons.}
	\label{training}
	\end{center}
\end{figure}

\begin{figure}[t]
	\begin{center}
	\includegraphics[width=7cm]{pictures/nlp_client_server2.png}
	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server.}
	\label{nlp_client_server}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/paraphrases.png}
	\caption{Users can enter paraphrases of a claim to help the entailment algorithm.}
	\label{paraphrases}
	\end{center}
\end{figure}

\begin{description}
\item[Explicit page marking:] The user explicitly marks a snippet on a page by selecting the snippet, and selecting ``mark as disputed'' from a context menu (Figure~\ref{mark_disputed}).

@@

\item[Client-side entailment:] The browser extension runs a simple textual entailment algorithm over all sentences on every web page the user browses, checking to see if any sentence on the page entails any claim in the database (Figure~\ref{nlp_client_server}). A user can enter additional paraphrases of a claim to help the entailment algorithm (Figure~\ref{paraphrases}). This is the implementation used by the currently released version of Dispute Finder.
\end{description}

@@

The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm that is a common baseline in NLP. It divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

@@

We performed three qualitative ``think aloud'' user studies. The aim of these studies was to inform the iterative design of the Dispute Finder tool. The studies were not intended to validate the design of Dispute Finder as being correct.

@@

For the first two studies, we recruited participants using Craigslist. We posted a message asking people to tell us how they used the web to form and promote their opinions, and used their responses to select people who we thought might fit our ``skeptical reader'' and ``activist'' personas. For the final study, we instead used people from our lab who we thought would be a good fit for our personas. The first study had twelve participants (five female, seven male), the second study had six participants (four female, two male), and the final study had six participants participants (all male).

Each batch of users was shown a different iteration of the Dispute Finder design. The first two batches used versions in which users marked snippets explicitly and the popup window for a claim showed an argumentation graph describing the structure of the different alternative points of view (Figure~\ref{popup_graph}). The final group used a version in which a textual entailment algorithm on the client was used to determine what to mark, and the popup window showed lists of sources that support or oppose the claim. We present the findings of the three user studies together. Where a comment refers to particular version we make this clear.

@@

We also conducted interviews with most of our user study participants, and five additional people, asking them how they use the web to form and promote their opinions.

@@

Responses were generally positive. Most of the participants expressed an interest in using the tool ``when it is more mature'' with some keen to use it in its current state.

\todo{Tye: say how many were keen to use the tool.}

Most participants said that they would want to use Dispute Finder to tell them when information they read was disputed (skeptical reader). One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''. A smaller number said they would be likely to enter claims they disagreed with (activist). One participant who was a political blogger was eager to mark things he thought were lies.

@@

%In the first study, a user could mark a snippet by 
%
%In the interface used in the first two studies, a user could mark a snippet by selecting it, right clicking on it, and clicking ``mark as disputed''. They were then prompted to either select an existing claim or create a new one.

When marking a snippet on a particular page, users often did not appreciate that a claim should apply to more than one snippet. Several users tried to create a new claim with exactly the same text as the snippet they were marking, and several users asked why they had to ``enter the text again''. Similarly, several users got confused when a snippet made two different disputed claims. The correct behavior is to mark the same text with two different claims, but several participants tried to create a new compound claim such as ``Global warming will cause X and Y''.

@@

In the first two studies, the popup interface for a claim showed an argumentation graph. This graph connected the graphs in our database using ``supports'' or ``opposes'' links, and allowed each claim to also be associated with supporting articles. When shown an argumentation graph for a claim, users seemed to have little difficulty navigating and understanding it and appreciated the ability to explore the structure of an argument and see how different claims were connected. One user said ``I can see myself getting addicted to this'', and another said ``it's very intuitive''.

Users seemed to have difficulty creating such graph structures however. Several users linked one claim as supporting another when it would have been more logically correct for them to both support a third claim. For example ``Global warming is causing more hurricanes'' does not support ``Global warming is causing rising sea levels'', but both support ``Global warming is causing problems''. Users correctly realized that the claims were related, but were not sure how best to connect them. Some users were confused by claims that had a ``because'' relationship rather than a ``supports'' or ``opposes'' relationship. For example ``America did not sign the Kyoto Protocol'' {\it because} ``Signing Kyoto would harm the US economy''. These findings are consistent with those of Isenmann and Reuter~\cite{Isenmann1997}.

@@

When using the article list interface (Figure~\ref{article_list}), several users got confused about whether an article supported or opposed a claim that was itself phrased in the negative. For example a user would mark an article that opposed global warming as opposing the claim ``global warming is bad'' because the article opposed global warming.

@@

Several users created claims that had ambiguous meanings. One user entered a disputed claim about ``Wood'', meaning the guitarist ``Ronnie Wood'' of the Rolling Stones. Similar problems occurred with claims that were specific to a particular country, or a particular point in time.

Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them or that they were expected to be knowledgeable about, but were less interested about applying it to pages about other topics, that they were less interested in. For topics that didn't affect them users felt that misinformation was ``not important enough to bother with'', or that they could ``afford to be misinformed''.

@@

\todo{Need to say that the argumentation graph contains all existing claims and that it was a simple ``supports"/``opposes'' graph.}

@@

As we discuss in this paper, our system requires multiple components to work in concert. Performing the tasks associated with these components well is a hard problem, and we do not yet claim to have an implementation that is is good enough to be compelling for most users. We do however believe that Dispute Finder attacks an interesting problem that, if solved well, could significantly improve the utility of the web.

@@
